Secure Composition of Robust and Optimising Compilers

### 2023-07-12 popl/main.tex
fix typo

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
\MPpost{
	this abstract fails in setting up the robustness argument.
	it'll be a good exercise for you to take inspiration from this, but then write something as concise but with a more direct focus on robust properties
}
% context
To ensure that secure applications do not leak their secrets, they are required to uphold several security properties such as spatial and temporal memory safety as well as criptographic constant time.
% need
Existing work shows how to enforce these properties individually, in an architecture-independent way, by using secure compiler passes that each focus on an individual property.
% task
Unfortunately, given two secure compiler passes that each preserve a possibly-different security property, there is no way to tell what kind of security property will the composition of those secure compilers preserve.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% \MPpost{
%   this abstract fails in setting up the robustness argument.
%   it'll be a good exercise for you to take inspiration from this, but then write something as concise but with a more direct focus on robust properties
% }
% context
To ensure that secure applications do not leak their secrets, they are required to uphold several security properties such as spatial and temporal memory safety as well as cryptographic constant time.
% need
Existing work shows how to enforce these properties individually, in an architecture-independent way, by using secure compiler passes that each focus on an individual property.
% task
Unfortunately, given two secure compiler passes that each preserve a possibly different security property, it is unclear what kind of security property the composition of those secure compiler passes preserve.
%there is no way to tell what kind of security property will the composition of those secure compilers preserve.
